\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-12 paper/main.tex
challenges

\textbf{Handling bugs from nighly builds requires saving wheels.}  Many
of the reproducible bugs rely on nightly builds of the
libraries. These builds are available for a limited amount of time. In
order to ensure bugs reported on these builds to remain reproducible,
it is imperative to save wheel files~\cite{wheels} for the
correspondind builds.

\textbf{Handling bugs in specific GPU-CUDA versions requires OS
  changes:} Many of the GPU-related bugs can only be reproduced with
library versions that are built with specific versions of CUDA.
These builds require those specific CUDA drivers to be installed on
the system, and the version of the CUDA driver installed on a system
can not be changed with Python's virtual enviroments.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
That is why we use Docker Containers with specific CUDA drivers to reproduce
such bugs instead of virtual enviroments.

>>>>

\textbf{Handling bugs from nighly builds requires saving wheels.}
Many of the reproducible bugs rely on the libraries' nightly builds,
which are available for a limited amount of time. To ensure that bugs
reported on these builds remain reproducible, it is necessary to save
Python wheel files (.whl)~\cite{wheels} for the correspondind builds.

\textbf{Handling bugs in specific GPU-CUDA versions requires OS
  changes:} Some GPU-related bug instances can only be reproduced with
specific versions of CUDA~\cite{cuda}, NVIDIA's platform and API for
programming GPUs. These instances require specific CUDA drivers to be
installed on the system. Python virtual enviroments are not designed
to enable change of OS drivers.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
We use Docker containers for the bug instances that require changes in
drivers.
